---
title: "Task 24/09"
author: "moi"
date: "10/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
require(RMySQL) || {install.packages("RMySQL"); require(RMySQL)}

con<-dbConnect(RMySQL::MySQL(),
               host      = "titlon.uit.no",
               user      = "gvi009@uit.no",
               password  = "RXHI5qI!MWfjzNlxcJp3S",
               db        = "OSE")

dbListTables(con)
dbListFields(con,"equity")
rs = dbSendQuery(con, "SELECT * FROM equity WHERE Name='Equinor'")
titlon_data=fetch(rs,-1)
# -------------------------------------------------------------------------

?fetch()

#' Congratulations, you are now connected to Titlon, and are ready to run SQL queries.
#' Our connection is labelled `con`.

library(tidyverse)

browseURL("https://rviews.rstudio.com/2017/05/17/databases-using-r/")

browseURL("https://db.rstudio.com/dplyr/")

#' A very useful function in DBI is dbListTables(), which retrieves the names of available tables.
#' In this case "con"
dbListTables(con)

#' Another useful function is the dbListFields, which returns a vector with all of the column names in a table.
dbListFields(con, "equity")

#' How many rows of data is there?
tally(tbl(con, "equity")) # could be useful to know before loading the data locally

#' Now that we've copied the data, we can use tbl() to take a reference to it:
#' This is probably the most important function so far.
equity <- tbl(con, "equity")
equity

#' We can now use dplyr lingo on this database object, end with collect() to retrieve data locally
names <- equity %>% select(Symbol, Name) %>% collect()
unique(names$Name)

#' Finding a specific Symbol
names %>% filter(Name=="Equinor")

#' Number of obsevations per symbol
table <- fct_count(names$Symbol)
table

#' How many sectors are there?
sectors <- equity %>% select(Sector) %>% collect()
fct_count(sectors$Sector)

#' When used against a database, the previous function is converted to a SQL query that works with MS SQL Server.
#' The `show_query()`` function displays the translation.
show_query(tally(tbl(con, "equity")))


#' 1) Use the "bonds" table.
bonds <- tbl(con, "bonds")
bonds

#' a) What are the variables in the "bonds" table?
dbListFields(con,"bonds")
#[1] "Date"             "FmDate"           "MaturityDate"     "SecurityId"       "CompanyId"       
#[6] "Name"             "Issuer"           "EqName"           "EqSecurityID"     "eqISIN"          
#[11] "ISINSubCode"      "BondType"         "Symbol"           "ISIN"             "CouponRate"      
#[16] "OpenPrice"        "High"             "Low"              "LastTradedPrice"  "OfficialVolume"  
#[21] "UnofficialVolume" "BestBidPrice"     "BestAskPrice"  

#' b) How many observations is there in the "bonds" table?
tally(tbl(con, "bonds"))
#4728421

#' c) Download the bonds table only for EqName "Norsk Hydro".
names <- bonds %>% select(Symbol, Name) %>% collect()
unique(names$Name)
names %>% filter(Name=="Norsk Hydro")

#' d) Fix the dates (hint: use lubridate package). Remove any duplicate dates.

#' 2) Use the "equity" table.
equity <- tbl(con, "equity")
equity

#' b) What are the variables in the "equity" table?
dbListFields(con,"equity")
# [1] "Date"                       "SecurityId"                 "CompanyId"                 
#[4] "Symbol"                     "ISIN"                       "Name"                      
#[7] "BestBidPrice"               "BestAskPrice"               "Open"                      
#[10] "High"                       "Low"                        "Close"                     
#[13] "OfficialNumberOfTrades"     "OfficialVolume"             "UnofficialNumberOfTrades"  
#[16] "UnofficialVolume"           "VolumeWeightedAveragePrice" "Price"                     
#[19] "AdjustedPrice"              "Dividends"                  "LDividends"                
#[22] "CorpAdj"                    "DividendAdj"                "Currency"                  
#[25] "Description"                "CountryCode"                "SumAnnualDividends"        
#[28] "NumberOfShares"             "CompanyOwnedShares"         "OutstandingShares"         
#[31] "Exchange"                   "NOKPerForex"                "mktcap"                    
#[34] "OSEBXmktshare_prevmnth"     "OSEBXAlpha_prevmnth"        "OSEBXBeta_prevmnth"        
#[37] "SMB"                        "HML"                        "LIQ"                       
#[40] "MOM"                        "DividendPriceRatio"         "lnDeltaP"                  
#[43] "lnDeltaOSEBX"               "lnDeltaOBX"                 "bills_DayLnrate"           
#[46] "Sector"

#' c) Extract Equinor and Norsk Hydro data from the equity database.
#' d) Fix the dates (hint: use lubridate package). Remove any duplicate dates.
#' e) Find the average AdjustedPrice per month, per stock, and plot it over time.
#' f) Plot the daily AdjustedPrice of these two stocks over time.
#' g) Plot the OfficialNumberOfTrades against the AdjustedPrice, using colors for each year.

