---
title: "Task 3 - 25/10"
author: "Gwendoline Viquesnel"
date: "10/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#Loading package
library(readr)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(lubridate)
```


```{r, include=FALSE}
#Opening and reading the files 2017 and 2018 in R with only value needed for the exercise
databirths2017 <- read_fwf("Nat2017",
           fwf_positions(start = c(475, 504, 9, 13),
                         end = c(475, 507, 12, 14),
                         col_names = c("sex","birthweight", "birthyear", "birthmonth")))

head(databirths2017)
           
databirths2018 <- read_fwf("Nat2018",
              fwf_positions(start = c(475, 504, 9, 13),
                         end = c(475, 507, 12, 14),
                         col_names = c("sex","birthweight", "birthyear", "birthmonth")))
      

head(databirths2018)
```

## The proportion of boys and girls in 2017 and 2018

```{r, include=FALSE}
# What is the average birth weight in grams?

Boys2017 <- databirths2017 %>% filter(sex == "M") %>% count()
Girls2017 <- databirths2017 %>% filter(sex == "F") %>% count()

proportionBoys2017 <- (Boys2017 / (Boys2017+Girls2017)) 
proportionGirls2017 <- (1 - proportionBoys2017) 

proportionBoys2017_2 <- round((proportionBoys2017 * 100), 2)
proportionGirls2017_2 <- round((proportionGirls2017 * 100), 2)

Boys2018 <- databirths2018 %>% filter(sex == "M") %>% count()
Girls2018 <- databirths2018 %>% filter(sex == "F") %>% count()

proportionBoys2018 <- (Boys2018 / (Boys2018+Girls2018))
proportionGirls2018 <- (1 - proportionBoys2018) 

proportionBoys2018_2 <- round((proportionBoys2018 * 100), 2)
proportionGirls2018_2 <- round((proportionGirls2018 * 100), 2)

```

*The proportion of girls in 2017 was `r proportionGirls2017_2`% (and boys was `r proportionBoys2017_2`%) whereas the proportion of girls in 2018 was `r proportionGirls2018_2`% (and boys was `r proportionBoys2018_2`%).*

## Average birth weight in grams of babies born in 2017 and 2018

```{r, include=FALSE}
# What is the average birth weight in grams?

databirths2017$birthweight <- as.numeric(databirths2017$birthweight)
databirths2018$birthweight <- as.numeric(databirths2018$birthweight)

averagebirthweight2017 <- mean(databirths2017$birthweight)
averagebirthweight2018 <- mean(databirths2018$birthweight)

```


*In 2017, the average birth weight was `r averagebirthweight2017` while in 2018 the average birth weight was `r averagebirthweight2018`*

## Density plot of the birth weight of both boys and girls born in 2018

```{r, echo=FALSE}
#Make a density plot on the birth weight between boys and girls in 2018. Is it different?

ggplot(databirths2018, aes(x=birthweight, fill=sex)) + geom_density() +  ggtitle("Birth weight comparison between boys and girls in 2018")

```


*We can notice that girls birth weight curve tends to be a bit higher than boys birth weight curve, meaning that girls birth weight tends to be lower than boys birth weight.*

# Average birth weight by month and year

```{r, echo=FALSE}
#Does the average birth weight vary by month and year?

# Group the two dataframe and the columns birthyear and birthmonth
databirths20172018 <- rbind(databirths2017, databirths2018) %>%
  unite("birthdate", birthyear, birthmonth, sep="/")

# Calculate the monthly mean weight 
averageweightmonthly <- databirths20172018 %>% group_by(birthdate) %>% summarize(averageweight = mean(birthweight))

averageweightmonthly$birthdate <- parse_date_time(averageweightmonthly$birthdate, "ym")

ggplot(averageweightmonthly) + geom_line(mapping = aes(x=birthdate, y=averageweight), stat="identity") +
  ggtitle("Average birth weight calculated monthly for the years 2017 and 2018") 
```


*We can notice that the average weight tends to be low for babies born in winter while it tend to be higher when babies are born in summer*


